---
title: "DAOH"
author: "Connor Sullivan"
date: "2021"
output: html_document
---

```{r}
library(lubridate)
library(tidyr)
library(dplyr)
library(stringr)
library(mice)
library(quantreg)
```

Reading in important libraries.

```{r}
#Reading in ANZDATA
master=read.csv("master.csv")
```

Reading in data from NMDS
```{r}
util=read.csv("util.csv")
```

Getting and formatting NMDS data so it can be added

```{r}
NMDS=data.frame(patientID=util$patient_id,
ethnicity=recode(util$ETHNICGP,"10"="European","11"="European","12"="European", "21"="NZM", "30"="Pacific","31"="Pacific","32"="Pacific","33"="Pacific","34"="Pacific","35"="Pacific","36"="Pacific","37"="Pacific","40"="Asian","41"="Asian","42"="Asian","43"="Asian","44"="Asian" ,.default="Other"), domcodes=util$DOM_CD)
NMDS=as.data.frame(NMDS%>%group_by(patientID)%>%filter(row_number()==1))
```

Reading in NZdep scores
```{r}
cau_dep=read.csv("CAU dep.csv")
dom_census=read.csv("dom census.csv")

cau_dep=data.frame(Description=cau_dep$CAU_name_2006, 
                   nzDep2006=cau_dep$CAU_average_NZDep2006,
                   nzDepScore2006=cau_dep$CAU_average_NZDep_score_2006)

dom_census=data.frame(domcodes=dom_census$dom, Description=dom_census$Description)

dom_census$domcodes=str_pad(dom_census$domcodes, 4, pad = "0")

dep=full_join(cau_dep, dom_census, by="Description")

#Manually setting values for typos in the joining description
dep=dep[1:2026,]
dep$domcodes[12]="0012"
dep$domcodes[104]="0113"
dep$domcodes[223]="0274"
dep$domcodes[369]="0499"
dep$domcodes[419]="0641"
dep$domcodes[509]="0807"
dep$domcodes[520]="1906"
dep$domcodes[624]="1007"
dep$domcodes[1026]="1640"
dep$domcodes[1425]="2311"
dep$domcodes[1426]="2312"
dep$domcodes[1504]="2524"
dep$domcodes[1534]="1122"
dep$domcodes[1758]="2822"
dep$domcodes[1801]="2908"
dep$domcodes[1865]="3022"
```

```{r}
#Creating play dataset
ANZDATA=data.frame(patientID=master$id, 
transplantDate=dmy(master$t0),
lastdate=dmy(master$lastfollowupdate),
time=master$aliveperiod,age=master$ageattransplant,male=master$gendercode,
bmi=master$bmi, smoking=recode(master$smoking, N=0, F=1, C=1), 
heartdisease=recode(master$coronaryarterycode, N=0, S=1, Y=1),
lungdisease=recode(master$chroniclungcode,N=0, S=1, Y=1),
peripheralvasc=recode(master$peripheralvascularcode,N=0, S=1, Y=1),
cerebrovascular=recode(master$cerebrovasularcode,N=0, S=1, Y=1),
diabetes=master$diabetescode,
currentAntibodies=master$maxcytotoxicantibodies,
lastTreatment=recode(master$lasttreatmentpretransplant,.default = "Haemodialysis", 
"APD"="Peritoneal dialysis", "CAPD"="Peritoneal dialysis",
"Pre-emptive transplant"="Pre-emptive transplant", 
"Own Kidney Function Recovered"="Own Kidney Function Recovered"),
dialysisTime=(as.integer(dmy(master$t0)-dmy(master$treatmentdate)))/365,
causeESKD=master$discat,dead=master$alivestatus,
ecd=recode(master$ecd, SCD=0, ECD=1), causeDeath=master$donorcauseofdeath,                donorAge=master$donorage,donorMale=master$donorgendercode,
donorHeight=master$donorheight, donorWeight=master$donorweight,
HLAmismatch=master$hlamismatch, HLA_A=master$hlamismatchesa,
HLA_B=master$hlamismatchesb, HLA_DR=master$hlamismatchesdr, ischemicTime=master$ischaemia, 
creat=master$creatinineterminal,KDRI=master$kdri, KDPI=master$kdpi,
donorHeartbeat=recode(master$heartbeatingcode, N=0, Y=1),
donorDiab=recode(master$donordiabetescode, N=0, P=1, T=1),
donorHyper=recode(master$hypertensioncode, N=0, Y=1), 
donorOlig=recode(master$oliguriacode, N=0, Y=1),
transplantCentre=master$transplantcentrecodeid, dual=master$dual)
```

Combining data bases
```{r}
data=full_join(ANZDATA, NMDS, by="patientID")%>%full_join(dep, by="domcodes")
data=as.data.frame(data%>%group_by(patientID)%>%filter(row_number()==1))
data=data[-1039,]
```

```{r}
data=subset(data, select = -c(domcodes, Description))

data$causeESKD=recode(data$causeESKD, "Diabetic Nephropathy"="Diabetic Nephropathy", .default = "Other")
data$diabetes=recode(data$diabetes, "N"=F, .default = T)

data$causeESKD=as.factor(data$causeESKD)
data$smoking=as.logical(data$smoking)
data$dead=as.logical(data$dead)
data$male=as.logical(data$male)
data$smoking=as.logical(data$smoking)
data$heartdisease=as.logical(data$heartdisease)
data$lungdisease=as.logical(data$lungdisease)
data$peripheralvasc=as.logical(data$peripheralvasc)
data$diabetes=as.factor(data$diabetes)
data$donorHeartbeat=as.logical(data$donorHeartbeat)
data$cerebrovascular=as.logical(data$cerebrovascular)
data$lastTreatment=as.factor(data$lastTreatment)
data$HLAmismatch=as.factor(data$HLAmismatch)
data$HLA_A=as.factor(data$HLA_A)
data$HLA_B=as.factor(data$HLA_B)
data$HLA_DR=as.factor(data$HLA_DR)
data$ecd=as.logical(data$ecd)
data$donorMale=as.logical(data$donorMale)
data$donorOlig=as.logical(data$donorOlig)
data$donorDiab=as.logical(data$donorDiab)
data$donorHyper=as.logical(data$donorHyper)
data$ethnicity=as.factor(data$ethnicity)
data$causeDeath=as.factor(data$causeDeath)
data$transplantCentre=as.factor(data$transplantCentre)
data$dual=as.factor(data$dual)
```

Reading in the data
```{r}
dates=data.frame(patientID=util$patient_id, transdate=dmy(util$TransplantDate)
                 ,eventstart=dmy(util$EVSTDATE), eventend=dmy(util$EVENDATE)
                 ,domCode=util$DOM_CD)
```

```{r}
deaths=data.frame(patientID=master$id,time=master$aliveperiod)
dates=dates %>% full_join(deaths, by="patientID")
dates=dates[1:length(util[,1]),]
```

Fixing dates. Changing dates as people died day before they left hospital. Then sorting.
```{r}
wrong_index=which(as.integer(dates$eventstart-dates$transdate)<0)
dates$eventstart[wrong_index]=dates$transdate[wrong_index]

dates$eventend[which(dates$patientID=="P9906946")]=dmy("28/09/2003")
dates$eventend[which(dates$patientID=="P9904011")]=dmy("26/07/2005")

dates=as.data.frame(dates%>%arrange(patientID,eventstart))
```

A function where it will return a vector of DAOH for a given number of days
```{r}
daysFunction=function(days){
  days=days
  index=1
  los_tot=c()
  while (index<length(dates[,1])) {
    patient=dates$patientID[index]
    count=0
    while(index+count+1<=length(dates[,1])&patient==dates$patientID[index+count+1]){
      dates$patientID[index+count+1]
      count=count+1
    }
    los=c()
    for (i in index:(index+count)) {
      if(as.integer(dates$eventend[i]-dates$transdate[i])<days){
        los[i-index+1]=as.integer(dates$eventend[i]-dates$eventstart[i])
      } else if(as.integer(dates$eventstart[i]-dates$transdate[i])<days){
        los[i-index+1]=days-(as.integer(dates$eventstart[i]-dates$transdate[i]))
      } else{
        break
      }
    }
    pat.index=which(dates$patientID==patient)
    if(dates$time[pat.index[1]]>days){
      tot=days-sum(los)
    } else{
      tot=days-(sum(los)+(days-dates$time[pat.index[1]]))
    }
    if(dates$time[index]<=days){
      tot=0
    }
    count=count+1
    los_tot=append(los_tot,rep(tot, count))
    index=index+count
  }
  return(los_tot)
}
```

DAOH for 28 days
```{r}
days28=daysFunction(28)
```

Making a DAOH dataframe
```{r}
DAOH=data.frame(days28)
final=data.frame("patientID"=dates$patientID, DAOH)
final=as.data.frame(final%>%group_by(patientID)%>%filter(row_number()==1))
```
People have multiple dom codes but only the dom code from first hospital visit is used.

Then join to NZdep with dom codes
```{r}
finaldf=final %>% full_join(data, by="patientID")

finaldf=finaldf[finaldf$transplantCentre!="H6540777",]
finaldf$transplantCentre=droplevels(finaldf$transplantCentre)
finaldf=subset(finaldf, select=-c(patientID, lastdate))
```

Looking at histograms
```{r}
hist(finaldf$days28, breaks=28, main="DAOH 28 days after transplantation", xlab="Days alive and out of hospital")
```

```{r}
boxplot(finaldf$days28~finaldf$ecd, main="Boxplot of DAOH28 split by ECD/SCD", xlab = "Extended Criteria Donor", ylab="DAOH28")
plot(jitter(finaldf$KDRI, 0.05), finaldf$days28)
plot(jitter(finaldf$KDPI, 0.05), finaldf$days28)

hist(finaldf$days28[finaldf$ecd==T], freq = FALSE)
hist(finaldf$days28[finaldf$ecd==F], freq = FALSE)
```

Fitting some linear models
```{r}
lm_ecd=lm(days28 ~ ecd, data = finaldf)
summary(lm_ecd)
plot(lm_ecd)

lm_KDRI=lm(days28 ~ KDRI, data = finaldf)
summary(lm_KDRI)
plot(lm_KDRI)

lm_KDPI.85=lm(days28 ~ KDPI>85, data = finaldf)
summary(lm_KDPI.85)
```



Fitting the quantile regressions
```{r}
ecd_uni_0.5 <- rq(days28 ~ ecd, tau = .5, data = finaldf)
summary(ecd_uni_0.5, se="boot", R=5000)

ecd_uni_0.75 <- rq(days28 ~ ecd, tau = .75, data = finaldf)
summary(ecd_uni_0.75, se="boot", R=5000)
```

Fitting ECD model for all quantiles
```{r}
ecd_uni_all <- rq(days28 ~ ecd, tau = seq(0.01, 0.99, length.out=98), data = finaldf)
plot(ecd_uni_all)
```


```{r}
KDRI_uni_0.5 <- rq(days28 ~ KDRI, tau = .5, data = finaldf)
summary(KDRI_uni_0.5, se="boot", R=5000)

KDRI_uni_0.75 <- rq(days28 ~ KDRI, tau = .75, data = finaldf)
summary(KDRI_uni_0.75, se="boot", R=5000)

```


```{r}
c(-1.79352-1.96*0.66751   ,-1.79352+1.96*0.66751   )
c(0-1.96*0.24208    ,0+1.96*0.24208    )

plot(finaldf$KDRI, finaldf$days28, main="KDRI and DAOH with quantile regression estimates", xlab="KDRI", ylab="DAOH")
abline(coef(KDRI_uni_0.5), col="red")
abline(coef(KDRI_uni_0.75), col=4)
legend("bottomright", legend = c("Median", "Upper Quartile"), col=c(2,4), lty=1)
```


Fitting KDRI model for all quantiles
```{r}
KDRI_uni_all <- rq(days28 ~ KDRI, tau = seq(0.01, 0.99, length.out=98), data = finaldf)
plot(KDRI_uni_all)
```


```{r}
KDPI_uni_0.5 <- rq(days28 ~ KDPI>85, tau = .5, data = finaldf)
summary(KDPI_uni_0.5, se="boot", R=5000)

KDPI_uni_0.75 <- rq(days28 ~ KDPI>85, tau = .75, data = finaldf)
summary(KDPI_uni_0.75, se="boot", R=5000)
```

```{r}
boxplot(finaldf$days28~finaldf$KDPI>85, main="Boxplot of DAOH28 split by KDPI", xlab = "KDPI above 85%", ylab="DAOH28")
```

Imputing the data
```{r}
imp_finaldf=subset(finaldf, select = -c(transplantDate, HLA_A, HLA_B, HLA_DR, time))

imp_finaldf$ethnicity=recode(imp_finaldf$ethnicity, "NZM"="NZM", "Pacific"="Pacific", .default = "Non-Maori/Non-Pacific")
imp_finaldf$lastTreatment=recode(imp_finaldf$lastTreatment, "Haemodialysis"="Haemodialysis", "Peritoneal dialysis"="Peritoneal dialysis", .default = "Pre-emptive transplant")
imp_finaldf$nzDep2006=cut(imp_finaldf$nzDep2006,breaks=c(-Inf, 5.5, 8.5, Inf), labels=c("1-5","6-8","9-10"))
imp_finaldf$transplantYear=cut(as.numeric(format(finaldf$transplantDate, "%Y")), 
                            breaks = c(-Inf,2002.5,2007.5,2012.5,Inf),
                            labels=c("1997-2002", "2003-2007", "2008-2012", "2013-2016"))
imp_finaldf$causeESKD=recode(imp_finaldf$causeESKD, "Not reported"="Unknown", "Uncertain"="Unknown")

imp=mice(imp_finaldf, m=5, maxit=20, seed=1, print=FALSE)
```


Complete Imp datasets
```{r}
imp1=complete(imp, 1)
imp2=complete(imp, 2)
imp3=complete(imp, 3)
imp4=complete(imp, 4)
imp5=complete(imp, 5)

imp1$KDPI=imp1$KDPI>85
imp2$KDPI=imp2$KDPI>85
imp3$KDPI=imp3$KDPI>85
imp4$KDPI=imp4$KDPI>85
imp5$KDPI=imp5$KDPI>85
```


```{r}
imp_ecd_0.5=with(imp, rq(days28 ~ ecd, tau = .5))
summary(pool(imp_ecd_0.5), se="boot", R=5000)

imp_ecd_0.75=with(imp, rq(days28 ~ ecd, tau = .75))
summary(pool(imp_ecd_0.75), se="boot", R=5000)
```

```{r}
imp_KDRI_0.5=with(imp, rq(days28 ~ KDRI, tau = .5))
summary(pool(imp_KDRI_0.5), se="boot", R=5000)

imp_KDRI_0.75=with(imp, rq(days28 ~ KDRI, tau = .75))
summary(pool(imp_KDRI_0.75), se="boot", R=5000)
```


```{r}
imp_KDPI_0.5=with(imp, rq(days28 ~ KDPI>85, tau = .5))
summary(pool(imp_KDPI_0.5), se="boot", R=5000)

imp_KDRI_0.75=with(imp, rq(days28 ~ KDRI>85, tau = .75)) #Error due to the data being binary
summary(pool(imp_KDRI_0.75), se="boot", R=5000)
```

Full model for median, ECD
```{r}
full_ecd_0.5=with(imp, rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .5))
summary(pool(full_ecd_0.5), se="boot")
```

Final ECD models with imputed datasets (First one)
```{r, warning=F}
ecd1_0.5=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .5, data = imp1)

ecd1_0.5_final=step(ecd1_0.5, trace=0, direction = "backward")

summary(ecd1_0.5_final)
```

```{r}
ecd1_0.5_final$formula
```

Second
```{r, warning=F}
ecd2_0.5=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .5, data = imp2)

ecd2_0.5_final=step(ecd2_0.5, trace=0, direction = "backward")
```

```{r}
ecd2_0.5_final$formula
```

Third
```{r, warning=F}
ecd3_0.5=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .5, data = imp3)

ecd3_0.5_final=step(ecd3_0.5, trace=0, direction = "backward")

AIC(ecd3_0.5_final)
AIC(rq(formula = days28 ~ ecd + age + ethnicity + causeESKD + nzDep2006 + 
    bmi + heartdisease + cerebrovascular + dialysisTime + ischemicTime + 
    HLAmismatch + currentAntibodies + transplantYear + transplantCentre, tau = 0.5, data = imp3))
```

```{r}
ecd3_0.5_final$formula
```


Fourth
```{r, warning=F}
ecd4_0.5=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .5, data = imp4)

ecd4_0.5_final=step(ecd4_0.5, trace=0, direction = "backward")

AIC(ecd4_0.5_final)
AIC(rq(days28 ~ ecd + age + ethnicity + causeESKD + nzDep2006 + bmi + 
    heartdisease + dialysisTime + ischemicTime + HLAmismatch + 
    currentAntibodies + transplantYear + transplantCentre ,  tau = .5, data = imp4))
```

```{r}
ecd4_0.5_final$formula
```


Fifth
```{r, warning=F}
ecd5_0.5=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .5, data = imp5)

ecd5_0.5_final=step(ecd5_0.5, trace=0, direction = "backward")

AIC(ecd5_0.5_final)
AIC(rq(days28 ~ ecd + age + ethnicity + causeESKD + nzDep2006 + bmi + 
    heartdisease + cerebrovascular + dialysisTime + ischemicTime + 
    HLAmismatch + currentAntibodies + transplantYear + transplantCentre ,  tau = .5, data = imp5))
```

```{r}
ecd5_0.5_final$formula
```

```{r}
ecd_0.5_final=with(imp, rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+heartdisease+diabetes+cerebrovascular+dialysisTime+ischemicTime+HLAmismatch+currentAntibodies+relevel(transplantYear, ref = 4)+transplantCentre+relevel(transplantYear, ref = 4)*ecd, tau = .5))
summary(pool(ecd_0.5_final), se="boot", R=5000)
```

```{r}
-0.805154534 -qnorm(0.975)*0.969308842 
-0.805154534 +qnorm(0.975)*0.969308842 

-2.829338172  -qnorm(0.975)*1.936988537  
-2.829338172  +qnorm(0.975)*1.936988537  

-0.569952316  -qnorm(0.975)*1.075511541  
-0.569952316  +qnorm(0.975)*1.075511541  

0.091237154  -qnorm(0.975)*1.088071405 
0.091237154 +qnorm(0.975)*1.088071405 
```

First for ECD 0.75
```{r, warning=F}
ecd1_0.75=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .75, data = imp1)

ecd1_0.75_final=step(ecd1_0.75, trace=0, direction = "backward")

summary(ecd1_0.75_final)
```

```{r}
ecd1_0.75_final$formula
```

Second
```{r, warning=F}
ecd2_0.75=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .75, data = imp2)

ecd2_0.75_final=step(ecd2_0.75, trace=0, direction = "backward")

summary(ecd2_0.75_final)

AIC(ecd2_0.75_final)

ecd2_0.75_final$formula

mod=rq(days28 ~ ecd + age + causeESKD + nzDep2006 + bmi + cerebrovascular + 
    dialysisTime + ischemicTime + HLAmismatch + transplantYear + 
    transplantCentre, tau = 0.75, data=imp2)
AIC(mod)
```

```{r}
ecd2_0.75_final$formula
```

Third
```{r, warning=F}
ecd3_0.75=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .75, data = imp3)

ecd3_0.75_final=step(ecd3_0.75, trace=0, direction = "backward")
```

```{r}
ecd3_0.75_final$formula
```


Fourth
```{r, warning=F}
ecd4_0.75=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .75, data = imp4)

ecd4_0.75_final=step(ecd4_0.75, trace=0, direction = "backward")

summary(ecd4_0.75_final)
```

```{r}
ecd4_0.75_final$formula
```


Fifth
```{r, warning=F}
ecd5_0.75=rq(days28~ecd+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ ecd*transplantYear+ecd*nzDep2006, tau = .75, data = imp5)

ecd5_0.75_final=step(ecd5_0.75, trace=0, direction = "backward")
```

```{r}
ecd5_0.75_final$formula
```


```{r}
ecd_0.75_final=with(imp, rq(days28 ~ ecd+age+male+causeESKD+nzDep2006+bmi+cerebrovascular+diabetes+dialysisTime+ischemicTime+HLAmismatch+transplantYear+transplantCentre+nzDep2006*ecd, tau=0.75))
summary(pool(ecd_0.75_final), se="boot", R=5000)
```

```{r}
-0.233922231-qnorm(0.975)*0.455214852
-0.233922231+qnorm(0.975)*0.455214852

-0.952522397-qnorm(0.975)*0.610813365  
-0.952522397+qnorm(0.975)*0.610813365  

0.345818259 -qnorm(0.975)*0.530472190   
0.345818259 +qnorm(0.975)*0.530472190   
```

Final KDRI models with imputed datasets (First one)
```{r, warning=F}
KDRI1_0.5=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .5, data = imp1)

KDRI1_0.5_final=step(KDRI1_0.5, trace=0, direction = "backward")
```

```{r}
KDRI1_0.5_final$formula
```

Second
```{r, warning=F}
KDRI2_0.5=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .5, data = imp2)

KDRI2_0.5_final=step(KDRI2_0.5, trace=0, direction = "backward")
```

```{r}
KDRI2_0.5_final$formula
```

Third
```{r, warning=F}
KDRI3_0.5=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .5, data = imp3)

KDRI3_0.5_final=step(KDRI3_0.5, trace=0, direction = "backward")
```

```{r}
KDRI3_0.5_final$formula
```


Fourth
```{r, warning=F}
KDRI4_0.5=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .5, data = imp4)

KDRI4_0.5_final=step(KDRI4_0.5, trace=0, direction = "backward")
```

```{r}
KDRI4_0.5_final$formula
```


Fifth
```{r, warning=F}
KDRI5_0.5=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .5, data = imp5)

KDRI5_0.5_final=step(KDRI5_0.5, trace=0, direction = "backward")
```

```{r}
KDRI5_0.5_final$formula
```

Full KDRI median model

```{r}
KDRI_0.5_final=with(imp, rq(days28 ~ KDRI+male+age+ethnicity+causeESKD+nzDep2006+bmi+heartdisease+cerebrovascular+diabetes+dialysisTime+ischemicTime+currentAntibodies+relevel(transplantYear, ref = 4)+transplantCentre+KDRI*relevel(transplantYear, ref = 4),tau=0.5))

summary(pool(KDRI_0.5_final), se="boot", R="5000")
```

```{r}
-1.613581468 -qnorm(0.975)*0.760213859
-1.613581468 +qnorm(0.975)*0.760213859

-3.289617060-qnorm(0.975)*1.484952724 
-3.289617060+qnorm(0.975)*1.484952724 

0.751629246 -qnorm(0.975)*0.992912171    
0.751629246 +qnorm(0.975)*0.992912171    

0.695081235 -qnorm(0.975)*0.966778660  
0.695081235 +qnorm(0.975)*0.966778660  
```

First for KDRI 0.75
```{r, warning=F}
KDRI1_0.75=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .75, data = imp1)

KDRI1_0.75_final=step(KDRI1_0.75, trace=0, direction = "backward")
```

```{r}
KDRI1_0.75_final$formula
```

Second
```{r, warning=F}
KDRI2_0.75=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .75, data = imp2)

KDRI2_0.75_final=step(KDRI2_0.75, trace=0, direction = "backward")
```

```{r}
KDRI2_0.75_final$formula
```

Third
```{r, warning=F}
KDRI3_0.75=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .75, data = imp3)

KDRI3_0.75_final=step(KDRI3_0.75, trace=0, direction = "backward")
```

```{r}
KDRI3_0.75_final$formula
```


Fourth
```{r, warning=F}
KDRI4_0.75=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .75, data = imp4)

KDRI4_0.75_final=step(KDRI4_0.75, trace=0, direction = "backward")
```

```{r}
KDRI4_0.75_final$formula
```


Fifth
```{r, warning=F}
KDRI5_0.75=rq(days28~KDRI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDRI*transplantYear+KDRI*nzDep2006, tau = .75, data = imp5)

KDRI5_0.75_final=step(KDRI5_0.75, trace=0, direction = "backward")
```

```{r}
KDRI5_0.75_final$formula
```

Final KDRI model, 75th percentile
```{r}
KDRI_0.75_final=with(imp, rq(days28 ~ KDRI+male+age+causeESKD+nzDep2006+bmi+diabetes+dialysisTime+HLAmismatch+transplantYear+transplantCentre,tau=0.75))

summary(pool(KDRI_0.75_final), se="boot", R="5000")
```

```{r}
-1.14202125-qnorm(0.975)*0.219554558
-1.14202125+qnorm(0.975)*0.219554558
```

Final KDPI models with imputed datasets (First one)
```{r, warning=F}
KDPI1_0.5=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+KDPI*transplantYear+KDPI*nzDep2006, tau = .5, data = imp1)

KDPI1_0.5_final=step(KDPI1_0.5, trace=0, direction = "backward")
```

```{r}
KDPI1_0.5_final$formula
```

Second
```{r, warning=F}
KDPI2_0.5=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+KDPI*transplantYear+KDPI*nzDep2006, tau = .5, data = imp2)

KDPI2_0.5_final=step(KDPI2_0.5, trace=0, direction = "backward")
```

```{r}
KDPI2_0.5_final$formula
```

Third
```{r, warning=F}
KDPI3_0.5=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDPI*transplantYear+KDPI*nzDep2006, tau = .5, data = imp3)

KDPI3_0.5_final=step(KDPI3_0.5, trace=0, direction = "backward")
```

```{r}
KDPI3_0.5_final$formula
```


Fourth
```{r, warning=F}
KDPI4_0.5=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDPI*transplantYear+KDPI*nzDep2006, tau = .5, data = imp4)

KDPI4_0.5_final=step(KDPI4_0.5, trace=0, direction = "backward")
```

```{r}
KDPI4_0.5_final$formula
```


Fifth
```{r, warning=F}
KDPI5_0.5=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDPI*transplantYear+KDPI*nzDep2006, tau = .5, data = imp5)

KDPI5_0.5_final=step(KDPI5_0.5, trace=0, direction = "backward")
```

```{r}
KDPI5_0.5_final$formula
```

Final for KDPI median

```{r}
KDPI_0.5_final=with(imp, rq(days28 ~ (KDPI>85)+male+age+ethnicity+causeESKD+nzDep2006+bmi+heartdisease+dialysisTime+currentAntibodies+relevel(transplantYear, ref = 4)+transplantCentre+(KDPI>85)*relevel(transplantYear, ref = 4),tau=0.5))

summary(pool(KDPI_0.5_final), se="boot", R="5000")
```

```{r}
-2.342982526 -qnorm(0.975)*0.583959762  
-2.342982526 +qnorm(0.975)*0.583959762  

-1.219093563  -qnorm(0.975)*2.228510343   
-1.219093563 +qnorm(0.975)*2.228510343   

1.992044760 -qnorm(0.975)*0.842308232      
1.992044760 +qnorm(0.975)*0.842308232      

2.374378455  -qnorm(0.975)*0.840272871    
2.374378455  +qnorm(0.975)*0.840272871    
```

First for KDPI 0.75
```{r, warning=F}
KDPI1_0.75=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDPI*transplantYear+KDPI*nzDep2006, tau = .75, data = imp1)

KDPI1_0.75_final=step(KDPI1_0.75, trace=0, direction = "backward")
```

```{r}
KDPI1_0.75_final$formula
```

Second
```{r, warning=F}
KDPI2_0.75=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDPI*transplantYear+KDPI*nzDep2006, tau = .75, data = imp2)

KDPI2_0.75_final=step(KDPI2_0.75, trace=0, direction = "backward")
```

```{r}
KDPI2_0.75_final$formula
```

Third
```{r, warning=F}
KDPI3_0.75=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDPI*transplantYear+KDPI*nzDep2006, tau = .75, data = imp3)

KDPI3_0.75_final=step(KDPI3_0.75, trace=0, direction = "backward")
```

```{r}
KDPI3_0.75_final$formula
```


Fourth
```{r, warning=F}
KDPI4_0.75=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDPI*transplantYear+KDPI*nzDep2006, tau = .75, data = imp4)

KDPI4_0.75_final=step(KDPI4_0.75, trace=0, direction = "backward")
```

```{r}
KDPI4_0.75_final$formula
```


Fifth
```{r, warning=F}
KDPI5_0.75=rq(days28~KDPI+age+male+ethnicity+causeESKD+nzDep2006+bmi+smoking+heartdisease+peripheralvasc+diabetes+cerebrovascular+lungdisease+dialysisTime+lastTreatment+ischemicTime+HLAmismatch+currentAntibodies+dual+transplantYear+transplantCentre+ KDPI*transplantYear+KDPI*nzDep2006, tau = .75, data = imp5)

KDPI5_0.75_final=step(KDPI5_0.75, trace=0, direction = "backward")
```

```{r}
KDPI5_0.75_final$formula
```

```{r}
KDPI_0.75_final=with(imp, rq(days28 ~ (KDPI>85)+male+age+causeESKD+nzDep2006+bmi+dialysisTime+HLAmismatch+transplantYear+transplantCentre,tau=0.75))

summary(pool(KDPI_0.75_final), se="boot", R="5000")
```

```{r}
-0.87245659-qnorm(0.975)*0.273187912 
-0.87245659+qnorm(0.975)*0.273187912 
```